Clause Size Reduction with \alluip Learning

### 2020-05-10 paper.tex
final pass, fix some typos and out-of-date stats

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{theorem}
\usepackage[T1]{fontenc}
% \usepackage[T1,hyphens]{url}
\usepackage{hyperref}
%\PassOptionsToPackage{hypnens}{url}

@@

    \Procedure{\stablealluip}{$C_1, \assertionTrail$}
    \State \textbf{if} ($|C_1| - \LBD(C_1) < \tgap$) \textbf{return} $C_1$\label{ln:control} 
    \State $\ntries$++\label{ln:try} 
    \State $C_i \gets C_1$
    \State $\dlevels \gets\mbox{}$ decision levels in $C_1$ in descending order\label{ln:init_loop}
        \Comment{These never change}
    \For{($i=1$; $i < |\dlevels|$; $i$++)}\label{ln:begin_level_loop}
         \Comment{skip the deepest level $\dlevels[0]$}
        \State $C_i\gets\mbox{}$\tryuiplevel($C_i$, $\dlevels[i]$) 
            \Comment{Try to reduce this level to UIP}
        \If{$\bigl|\{\ell\,|\,\ell \in C_i \land \dlevel{\ell} \geq
            \dlevels[i]\}\bigr| + (|\dlevels| - (i+1)) \geq
            |C_1|$}\label{ln:earlyTerminate}
            \State \textbf{return} $C_1$ 
                \Comment{can't generate smaller clause}\label{ln:end_level_loop}
        \EndIf
   \EndFor
   \If{$\mathbf{\allUipPure} \in \config$}
       \State $C_i \gets \mathbf{minimize}(C_i)$\label{ln:puremin}
   \EndIf
   \If{$\bigl(|C_i| < |C_1| \land 
       \mathbf{\allUipAct}\in\config\implies(\code{AvgVarAct}(C_i) > \code{AvgVarAct}(C_1))$
      \label{ln:activity}}
        \State $\nsuc$++, \textbf{return} $C_i$  \label{ln:returnmin}\label{ln:suc}
        \Comment{$C_i$ is smaller than the input clause}
   \Else \State \textbf{return} $C_1$
   \EndIf
%    \State \textbf{return} \textbf{if} $|C_i| < |C_1|$) 
%           \textbf{then}  $C_i$ \textbf{else}  $C_1$
\EndProcedure
\Statex 
\Procedure{\tryuiplevel}{$C_i$, $i$}
    \Comment{Do not add new decision levels}
    \State $\ctry = C_i$
    \State $L_i = \left\{\ell \left| \ell \in \ctry 
                         \land \dlevel{l} = i\right.\right\}$\label{ln:litsati1}
    \While{$|L_i| > 1$}
        \State $p \gets\mbox{}$ \textbf{remove} lit with the highest trail index from $L_i$ 
        \If{($\exists q \in \reason{\lnot p}.\, \dlevel{q} \not \in \mathit{decLvls}$)}\label{ln:newdlevel}
        \Comment{Would add new decision levels}
             \If{($\mathbf{\allUipPure}\in \config$)}
                 \State \textbf{return} $C_i$ \Comment{Abort, can't UIP this level}
             \ElsIf{($\mathbf{\allUipMin}\in\config$)}
                 \State \textbf{continue} \Comment{Don't try to resolve away $p$}
             \EndIf
        \Else\label{ln:nonewdlevel}
            \State $\ctry \gets \ctry \resolve \reason{\lnot p}$
            \State $L_i = L_i \cup \{\ell\,|\, 
                                     \ell\in\reason{\lnot p} \land \ell\neq \lnot p \land \dlevel{\ell} = i
                                    \}$\label{ln:litsati2}
        \EndIf
     \EndWhile
    \State \textbf{return} $\ctry$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

%\allUipPure cannot trigger this early termination
%condition (it cannot increase the size of any processed level), but
%\allUipMin can.

@@

In sum, the two modified variable activity update schemes we
experimented with were
\[
    \begin{array}{l}
    \textbf{\allUipIn} \equiv \forall l\in C_i - C_1.\,\mathit{bumpActivity}l) \\
    \textbf{\allUipEx} \equiv \forall l\in C_i - C_1.\,\mathit{bumpActivity}(l) \land\mbox{} \\
    \qquad \forall l\in C_1 - C_i.\,\mathit{unbumpActivity(l)}
  \end{array}
\]

@@

\section{Implementation and Experiments}
%\subsubsection{Clause Reduction with $\stablealluip$.}
We implemented $\stablealluip$ learning schemes on \text{\MapleBase}
\cite{liang2016maple}, the winner of SAT Race 2016 application
track. We then evaluated these schemes and compare against the \oneuip
baseline on the full set of benchmarks from SAT RACE 2019 main track
which contains 400 instances. We ran our experiments on 2.70 GHz
XeonE5-2680 CPUs, allowing
%\fb{insert time bound}
5000 seconds per instance and a maximum of 12 GB memory.
%\fb{insert RAM bound}.

%\fb{Delete figure 2 and use only figure 8 with all of the
%  solvers. First briefly comment on the performance and make a brief observation about clause sizes.
 %Then have a new subsubsection that looks at clause sizes wrt. to the
  %two schemes \allUipPure and \allUipMin. Shrink fig 3 and 4 and put
  %them side by side (using a tabular environment as I did in figure 1).

  %Remove fig 5 and put those numbers in the text instead of in a table
  %as part of your discussion.

  %Then have a new subsubsection on DRAT trim and get rid of Fig 7.

  %Then a subsubsection on \stablealluip in modern solvers. Some of our
  %observations have no solid foundation, so check them to make sure
  %that you are just not stating your intuitions without reasonable
  %evidence. We need to to fit into 15 pages total along with a short
  %1/3 page for conclusions.

  %Finally add all citations.

  %If we add the more complex \allUipMin we also will need more space
  %to describe that, so prune some of your conclusions especially those
  %that are simply conjectures.
%}

@@

%Beside solved instances count and PAR-2 score, we additionally measure
%the average clause size. 
%and clause reduction ratio (both cumulative
%and non-cumulative)\footnote{The cumulative reduction ratio is
%  obtained through learning all clauses with the target learning
%  scheme; Therefore, the reduction is cumulative. The %non-cumulative
%  reduction ratio is obtained by running the target scheme for
%  measurement only (the minimized \oneuip clause is learned); Therefore,
%  the reduction is not cumulative. }  for each instances. 
%For $\MapleIUIPPure$ and $\MapleIUIMin$, we also captures the $\stablealluip$
%learning attempted rate and success rate.

%\begin{figure} 
%\begin{center}
%\begin{tabular}{ | m{3.3cm} | m{2cm}| m{2cm} | m{2cm} | m{2.7cm} | } 
%\hline
%Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
%\hline
%$\MapleBase$ & 221 (132, 89) & 5018.89 & 62.6 & 36.53\% \\ 
%\hline
%$\MapleIUIPPure$ & \textbf{228} (135, 93) & \nf{4867.37} & 49.88 & 41.6\%  (42.72\%)\\ 
%\hline
%$\MapleIUIMin$ & 226 (135, 91) & 4890.67 & \textbf{45.2} & \textbf{47.8\% (51.19\%)}\\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Benchmark results of $\MapleBase$ , $\MapleIUIPPure$  and $\MapleIUIMin$ on SAT2019 %race main track.
%CL Reduction\% is the clause size reduction ratio comparing to non-minimized \oneuip clauses, %and the values in the brackets are the non-cumulative reduction ratio.}
%\label{fig:t1}
%\end{figure}

%Fig.~\ref{fig:t1} shows that $\allUipPure$ ($\allUipPure$) solved seven
%(five) more instances than the baseline solver with lower PAR-2
%scores. $\allUipPure$ has marginally lower PAR-2 score than
%$\allUipPure$. Both $\allUipPure$ and $\allUipMin$ produce clause with
%significantly smaller size than \oneuip by 20.4\% and 27.7\%,
%respectively. Fig.~\ref{fig:len_pdf} shows the probability density
%distribution (PDF) of the relative clause size of both i-uip learning
%schemes ($\allUipPure$ in red and $\allUipMin$ in green) for each
%instance. $\allUipPure$ ($\allUipMin$) produces shorter clauses for 77.7\%
%(88.5\%) of instances, and average relative reduction from \oneuip is
%16.7\% (18.6\%). Fig.~\ref{fig:len_compare} compares the absolute
%clause size of $\allUipMin$, $\allUipPure$ and \oneuip, and it shows that
%both i-UIP learning schemes in general produce the smaller clauses,
%and the size reduction is more significant for instances with large
%average \oneuip clause size. Moreover, $\allUipMin$ clauses (indicated in
%5green) is consistently smaller than $\allUipPure$ clauses.

%\nf{ Do we need this?  We additionally looked at the 14 instances
%  solved by $\allUipMin$ but not by \oneuip. $\allUipMin$ produces smaller
%  clauses for all of them with average relative reduction of 22\% and
%  maximum 77\% (30 vs 135). Seven out of 14 instances has size
%  relative reduction over 30\%. For the 9 instances solved by \oneuip
%  but not by $\allUipMin$, $\allUipMin$ only produce smaller clause for
%  three instances and with average relative reduction of 3.3\%.}

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & $\stablealluip$ attempt rate & $\stablealluip$ success rate  \\ 
%\hline
%$\MapleIUIPPure$ & 16.1\% & 43.4\% \\ 
%\hline
%$\MapleIUIMin$ & 28.8\% & 59.3\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Compare $\allUipPure$ and $\allUipMin$ i-uip attempt rate and success rate. %$\allUipMin$ scheme attempted $\stablealluip$ more frequently, and it is more likely to %successfully produce smaller $C_i$ clause .}
%\label{fig:t2}
%\end{figure}

@@

%Fig.~\ref{fig:proof_compare} shows the
%absolute proof size comparison between $\allUipMin$ and \oneuip, and displays a similar trend %as the clause size comparison plot in Fig.~\ref{fig:len_compare}.

%\begin{figure} 
%\begin{center} 
%\begin{tabular}{ | m{3.5cm} | m{5cm}| m{3.5cm} | } 
%\hline
%Solver & optimized proof size (MB) & relative reduction size  \\ 
%\hline
%$\MapleBase$ & 613.9 & 0  \\ 
%\hline
%$\MapleIUIPPure$ & 487.2 & 6.90\% \\ 
%\hline
%$\MapleIUIMin$ & 413.2 & 17.18\% \\ 
%\hline
%\end{tabular}
%\end{center}
%\caption{Optimized UNSAT proof comparison for \oneuip $\allUipPure$ and $\allUipMin$. %Optimized proof size measures the average absolute proof size in MB, and relative reduction %size measures the average relative reduction for all UNSAT instances.}
%\label{fig:t3}
%\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics[width=0.8\textwidth]{figures/proof_size_compare.pdf}
%    \caption{Average optimized proof size between 1-uip and $\allUipMin$.}
%    \label{fig:proof_compare}
%\end{figure}

%\subsection{$\stablealluip$ as a Practical Learning Scheme}
%To evaluate $\stablealluip$'s effectiveness as a clause learning scheme, we
%re-implement $\allUipMin$ on $\MapleBase$ with the extensions mentioned
%in section~\ref{sec:i-uip}. We evaluated \oneuip learning and five
%$\stablealluip$ configurations ( $\allUipMin$, $\allUipPure$, $\allUipAct$,
%$\allUipIn$, and $\allUipEx$) on the SAT Race 2019 main track
%benchmark and reported solved instances, PAR-2 score and average
%clause size.

%Fig.~\ref{fig:t4} summarizes the result of the experiment. Learning
%scheme $\allUipPure$ solved the most overall instances (228) and the
%most UNSAT instances (93). $\allUipAct$ had the lowest PAR-2
%score. $\allUipIn$ solved the most SAT instances (138). $\allUipEx$
%produced the shortest average clause size, but solved the second least
%instances, one more instance than the baseline \oneuip learning. All
%configurations of $\stablealluip$ outperformed the baseline \oneuip scheme in
%solved instances, PAR-2 score and average clause size.

\begin{figure} 
\begin{center}
\fss{8pt}{10pt}
% \begin{tabular}{ | m{3.7cm} | m{4cm}| m{2cm} | m{2.75cm} |  }
\begin{tabular}{|l|l|l|l|} 
\hline
Solver & \#solved (SAT, UNSAT) $\Delta$ & PAR-2 & avg. clause Size \\ 
\hline
SAT 2017 Winner & & & \\
$\MapleSeven$ & 232 (135, 97) & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-all-pure & \textbf{244 (146, 98)} +12 & \textbf{4504.18} & 43.76 \\
\hline
$\MapleSeven$-all-min & 240 (144, 96) +8 & 4601.25 & \textbf{36.97} \\ 
\hline
$\MapleSeven$-all-act & 237 (140, 97) +5 & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-all-inclusive & 234 (137, 97) +2 & 4718.03 & 37.96 \\
\hline
\hline
SAT 2018 Winner & & & \\
$\MapleEightShort$ & 236 (138, 98) & 4671.81 & 61.69 \\
\hline
$\MapleEightShort$-all-pure & \textbf{241} (\textbf{142, 99}) +5 & \textbf{4598.18} & 44.19 \\
\hline
$\MapleEightShort$-all-min & 236 (141, 95) +0 & 4683.92 & 38.05 \\ 
\hline
$\MapleEightShort$-all-act & 240 (141, \textbf{99}) +4 & 4626.99 & 41.16 \\
\hline
$\MapleEightShort$-all-inclusive & 240 (\textbf{142}, 98) +4 & 4602.13 & \textbf{37.52} \\
\hline
\hline
SAT 2019 Winner & & & \\
$\MapleNineShort$ & 238 (140, \textbf{98}) & 4531.24 & 60.91 \\
\hline
$\MapleNineShort$-all-pure & 240 (142, \textbf{98}) +2 & 4519.08 &  43.32\\
\hline
$\MapleNineShort$-all-min & 244 (\textbf{148}, 96) +6 & \textbf{4419.84} & \textbf{36.88} \\
\hline
$\MapleNineShort$-all-act & 243 (146, 97) + 5 & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-all-inclusive & \textbf{243} (\textbf{148}, 95) +5 & 4455.76 & 37.02 \\
\hline
\hline
SAT 2019 Competitor & & &\\
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-all-pure & 235 (136, 99) $-$2  & 4668.96 & 48.26 \\
\hline
$\expSATShort$-all-min & 241 (143, 98) +4 & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-all-act & 244 (143, \textbf{101}) +7 & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-all-inclusive & \textbf{245} (\textbf{146}, 99) +8 & 4475.76 & \textbf{45.33}
\\
\hline
\hline
 & & &\\
$\defaultcadical$ & 249 (150, 99)  & \textbf{4311.76} & 101.96 \\
\hline
$\defaultcadical$-all-pure & 248 (151, 97) $-$1  & 4373.38 & 82.44  \\
\hline
$\defaultcadical$-all-min & 248 (149, 99) $-$1 & 4398.31 & 46.29 \\ 
\hline
$\defaultcadical$-all-act & \textbf{252} (\textbf{152}, \textbf{100}) +3 & 4331.56 & 47.34 \\
\hline
$\defaultcadical$-all-inclusive & 251 (\textbf{153}, 98) +2 & 4335.88 & \textbf{42.61}
\\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of \oneuip, $\allUipPure$. $\allUipMin$, $\allUipAct$ and $\allUipIn$ on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

\subsubsection{$\stablealluip$ in Modern SAT solvers.}
\begin{sloppypar}
To validate $\stablealluip$ as a practical learning scheme for modern
SAT solvers, we implemented $\stablealluip$ in the winners of 2017,
2018 and 2019 SAT Race
\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$ \cite{MdSolimul2019expMalpe} ($\expSATShort$)
and $\cadical$~\cite{cadical} solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We chose $\cadical$ because its default configuration\footnote{$\cadical$'s default configuration is different from the specialized 'sat' configuration, which solved the most SAT instances in the 2019 SAT Race.} (denote as $\defaultcadical$) solved 244 total instances in 2019 SAT Race, the highest among all participants. For this experimented, we used the latest version of $\defaultcadical$ instead of the SAT Race participant~\cite{Armin2019Cadical}.  We compared these solver's base \oneuip learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\stablealluip$
variants, $\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main
track benchmark. We report solved instances, PAR-2 score and the
average clause size.
\end{sloppypar}

Table~\ref{fig:t5} shows the benchmark result of the $\stablealluip$
configurations in our suite of modern solvers. Overall, we observed
similar performance gain on all modern solvers as we have seen on
$\MapleBase$ in Fig.~\ref{fig:t4}. More specifically, almost all
configurations improved on solved instance (+4.5 instances in average)
and PAR-2 score ($-$83.6 in average).  The average clause size
reduction is consistent across all solvers. Each configuration also
exhibits different strength: $\allUipPure$ solved the most instances
with the best PAR-2 score on two solvers, $\allUipMin$ yields small
clauses, $\allUipIn$ solved the most SAT instances, and $\allUipAct$
has stable performance.

On the SAT 2017 race winner $\MapleSeven$, all four configurations of
$\stablealluip$ outperformed \oneuip learning by 12, 8, 5, and 2 instances,
respectively. $\allUipPure$ solved more UNSAT and SAT instances while
the other configurations improved on solving SAT instances. The clause
size reduction of $\stablealluip$ is more significant on $\MapleSeven$
than on to $\MapleBase$.
%This may suggests that $\stablealluip$ and the recent
%learnt clause minimization approach~\cite{} synergies well because
%i-UIP clauses are shorter with more common literals which allows
%vivification~\cite{} to prune literals more aggressively through unit
%propagation.

The SAT 2018 race winner$\MapleEightShort$ uses chronological
backtracking (CB) for long distance backtracks. Three out of four
$\stablealluip$ configurations outperformed \oneuip by 5, 4 an 4 instances,
respectively.
%$\MapleEightShort$ improved from $\MapleSeven$ by using
%chronological backtracking (CB) for long distance
%backtracks. Therefore, we used $\stablealluip$-CB extension for all $\stablealluip$
%configurations.

%The results indicates that the improvement of $\stablealluip$
%is slightly shadowed by the adoption of CB. More specifically, we
%believe CB prevents decision levels from being compressed through the
%process of backtracking and literal assertion. The shorter i-UIP
%clauses can bring related literals closer, which in turns compresses
%the assertion stack and the decision levels. However, since CB
%discourages long distance backtracking, the effect of learning shorter
%clauses is shadowed until a full restart.  We believe we have observed
%an interesting interaction effect that shows the limitations of both
%CB and $\stablealluip$ learning for future research.

@@

%One possible explanation is that
%$\stablealluip$ learning can reduce an \oneuip clause to different i-UIP clauses
%for different assertion trails. Therefore, the solver is less likely
%to learn the same i-UIP clauses.

@@

$\defaultcadical$ with \oneuip solved 249 total instances, 5 more than the result from the SAT 2019 Race.  Applying $\allUipAct$ and $\allUipIn$ further improved the solved instance by 3 an 2, respectively.  The average learnt clause size of \oneuip on $\defaultcadical$ is much larger than other solvers' (101 vs 60) while the average clause size of $\stablealluip$ configurations are similar for all solvers.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xspace}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{theorem}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

@@

    \Procedure{\stablealluip}{$C_1, \assertionTrail$}
    \State \textbf{if} ($|C_1| - \LBD(C_1) < \tgap$) \textbf{return} $C_1$\label{ln:control} 
    \State $\ntries$++\label{ln:try} 
    \State $C_i \gets C_1$
    \State $\dlevels \gets\mbox{}$ decision levels in $C_1$ in descending order\label{ln:init_loop}
        \Comment{These never change}
    \For{($i=1$; $i < |\dlevels|$; $i$++)}\label{ln:begin_level_loop}
         \Comment{skip the deepest level $\dlevels[0]$}
        \State $C_i\gets\mbox{}$\tryuiplevel($C_i$, $\dlevels[i]$) 
            \Comment{Try to reduce this level to UIP}
        \If{$\bigl|\{\ell\,|\,\ell \in C_i \land \dlevel{\ell} \geq
            \dlevels[i]\}\bigr| + (|\dlevels| - (i+1)) \geq
            |C_1|$}\label{ln:earlyTerminate}
            \State \textbf{return} $C_1$ 
                \Comment{can't generate smaller clause}\label{ln:end_level_loop}
        \EndIf
   \EndFor
   \If{$\mathbf{\allUipPure} \in \config$}
       \State $C_i \gets \mathbf{minimize}(C_i)$\label{ln:puremin}
   \EndIf
   \If{$\bigl(|C_i| < |C_1| \land 
       \mathbf{\allUipAct}\in\config\implies(\code{AvgVarAct}(C_i) > \code{AvgVarAct}(C_1))$
      \label{ln:activity}}
        \State $\nsuc$++, \textbf{return} $C_i$  \label{ln:returnmin}\label{ln:suc}
        \Comment{$C_i$ is smaller than the input clause}
   \Else \State \textbf{return} $C_1$
   \EndIf
\EndProcedure
\Statex 
\Procedure{\tryuiplevel}{$C_i$, $i$}
    \Comment{Do not add new decision levels}
    \State $\ctry = C_i$
    \State $L_i = \left\{\ell \left| \ell \in \ctry 
                         \land \dlevel{l} = i\right.\right\}$\label{ln:litsati1}
    \While{$|L_i| > 1$}
        \State $p \gets\mbox{}$ \textbf{remove} lit with the highest trail index from $L_i$ 
        \If{($\exists q \in \reason{\lnot p}.\, \dlevel{q} \not \in \mathit{decLvls}$)}\label{ln:newdlevel}
        \Comment{Would add new decision levels}
             \If{($\mathbf{\allUipPure}\in \config$)}
                 \State \textbf{return} $C_i$ \Comment{Abort, can't UIP this level}
             \ElsIf{($\mathbf{\allUipMin}\in\config$)}
                 \State \textbf{continue} \Comment{Don't try to resolve away $p$}
             \EndIf
        \Else\label{ln:nonewdlevel}
            \State $\ctry \gets \ctry \resolve \reason{\lnot p}$
            \State $L_i = L_i \cup \{\ell\,|\, 
                                     \ell\in\reason{\lnot p} \land \ell\neq \lnot p \land \dlevel{\ell} = i
                                    \}$\label{ln:litsati2}
        \EndIf
     \EndWhile
    \State \textbf{return} $\ctry$
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

@@

In sum, the two modified variable activity update schemes we
experimented with were
\[
    \begin{array}{l}
    \textbf{\allUipIn} \equiv \forall l\in C_i - C_1.\,\mathit{bumpActivity}(l) \\
    \textbf{\allUipEx} \equiv \forall l\in C_i - C_1.\,\mathit{bumpActivity}(l) \land\mbox{} \\
    \qquad \forall l\in C_1 - C_i.\,\mathit{unbumpActivity(l)}
  \end{array}
\]

@@

\section{Implementation and Experiments}
We implemented $\stablealluip$ learning schemes on \text{\MapleBase}
\cite{liang2016maple}, the winner of SAT Race 2016 application
track. We then evaluated these schemes and compare against the \oneuip
baseline on the full set of benchmarks from SAT RACE 2019 main track
which contains 400 instances. We ran our experiments on 2.70 GHz
XeonE5-2680 CPUs, allowing
5000 seconds per instance and a maximum of 12 GB memory.

@@

@@

\begin{figure} 
\begin{center}
\fss{8pt}{10pt}
\begin{tabular}{|l|l|l|l|} 
\hline
Solver & \#solved (SAT, UNSAT) $\Delta$ & PAR-2 & avg. clause Size \\ 
\hline
SAT 2017 Winner & & & \\
$\MapleSeven$ & 232 (135, 97) & 4755.96 & 61.9  \\ 
\hline
$\MapleSeven$-all-pure & \textbf{244 (146, 98)} +12 & \textbf{4504.18} & 43.76 \\
\hline
$\MapleSeven$-all-min & 240 (144, 96) +8 & 4601.25 & \textbf{36.97} \\ 
\hline
$\MapleSeven$-all-act & 237 (140, 97) +5 & 4678.434 & 43.62 \\ 
\hline
$\MapleSeven$-all-inclusive & 234 (137, 97) +2 & 4718.03 & 37.96 \\
\hline
\hline
SAT 2018 Winner & & & \\
$\MapleEightShort$ & 236 (138, 98) & 4671.81 & 61.69 \\
\hline
$\MapleEightShort$-all-pure & \textbf{241} (\textbf{142, 99}) +5 & \textbf{4598.18} & 44.19 \\
\hline
$\MapleEightShort$-all-min & 236 (141, 95) +0 & 4683.92 & 38.05 \\ 
\hline
$\MapleEightShort$-all-act & 240 (141, \textbf{99}) +4 & 4626.99 & 41.16 \\
\hline
$\MapleEightShort$-all-inclusive & 240 (\textbf{142}, 98) +4 & 4602.13 & \textbf{37.52} \\
\hline
\hline
SAT 2019 Winner & & & \\
$\MapleNineShort$ & 238 (140, \textbf{98}) & 4531.24 & 60.91 \\
\hline
$\MapleNineShort$-all-pure & 240 (142, \textbf{98}) +2 & 4519.08 &  43.32\\
\hline
$\MapleNineShort$-all-min & 244 (\textbf{148}, 96) +6 & \textbf{4419.84} & \textbf{36.88} \\
\hline
$\MapleNineShort$-all-act & 243 (146, 97) + 5 & 4476.73 & 40.65 \\
\hline
$\MapleNineShort$-all-inclusive & \textbf{243} (\textbf{148}, 95) +5 & 4455.76 & 37.02 \\
\hline
\hline
SAT 2019 Competitor & & &\\
$\expSATShort$ & 237 (137, 100)  & 4628.96 & 63.19 \\
\hline
$\expSATShort$-all-pure & 235 (136, 99) $-$2  & 4668.96 & 48.26 \\
\hline
$\expSATShort$-all-min & 241 (143, 98) +4 & 4524.28 & 46.29 \\ 
\hline
$\expSATShort$-all-act & 244 (143, \textbf{101}) +7 & \textbf{4460.92} & 47.25 \\
\hline
$\expSATShort$-all-inclusive & \textbf{245} (\textbf{146}, 99) +8 & 4475.76 & \textbf{45.33}
\\
\hline
\hline
 & & &\\
$\defaultcadical$ & 249 (150, 99)  & \textbf{4311.76} & 101.96 \\
\hline
$\defaultcadical$-all-pure & 248 (151, 97) $-$1  & 4373.38 & 82.44  \\
\hline
$\defaultcadical$-all-min & 248 (149, 99) $-$1 & 4398.31 & 43.93 \\ 
\hline
$\defaultcadical$-all-act & \textbf{252} (\textbf{152}, \textbf{100}) +3 & 4331.56 & 47.34 \\
\hline
$\defaultcadical$-all-inclusive & 251 (\textbf{153}, 98) +2 & 4335.88 & \textbf{42.61}
\\
\hline
\end{tabular}
\end{center}
\caption{Benchmark results of \oneuip, $\allUipPure$. $\allUipMin$, $\allUipAct$ and $\allUipIn$ on SAT2019 race main track.}
\label{fig:t5}
\end{figure}

\subsubsection{$\stablealluip$ in Modern SAT solvers.}
\begin{sloppypar}
To validate $\stablealluip$ as a practical learning scheme for modern
SAT solvers, we implemented $\stablealluip$ in the winners of 2017,
2018 and 2019 SAT Race
\cite{DBLP:conf/ijcai/LuoLXML17,ryvchin2018maple,Stepan2019MapleLCMDistChronoBT}
and in the $\expSAT$ \cite{MdSolimul2019expMalpe} ($\expSATShort$)
and $\cadical$~\cite{cadical} solver. $\expSATShort$ is a top ten solver from 2019 SAT race which
uses random walk simulation to help branching. We chose $\expSATShort$
because (1) it is one of the top solvers in the 2019 SAT Race that does
not use chronological backtracking; and (2) the random walk simulation
branching heuristic is different from local branching heuristic (VSIDS
and LRB) that we have considered in $\allUipAct$, $\allUipIn$, and
$\allUipEx$. We chose $\cadical$ because its default configuration\footnote{$\cadical$'s default configuration is different from the specialized 'sat' configuration, which solved the most SAT instances in the 2019 SAT Race.} (denote as $\defaultcadical$) solved 244 total instances in 2019 SAT Race, the highest among all participants. For this experimented, we used the latest available version of $\defaultcadical$ instead of the 2019 SAT Race participant~\cite{Armin2019Cadical}.  We compared these solver's base \oneuip learning scheme
with $\allUipPure$, $\allUipMin$ and the top two $\stablealluip$
variants, $\allUipAct$ and $\allUipIn$, on the SAT Race 2019 main
track benchmark. We report solved instances, PAR-2 score and the
average clause size.
\end{sloppypar}

Table~\ref{fig:t5} shows the benchmark result of the $\stablealluip$
configurations in our suite of modern solvers. Overall, we observed
similar performance gain on all modern solvers as we have seen on
$\MapleBase$ in Fig.~\ref{fig:t4}. More specifically, almost all
configurations improved on solved instance (+3.9 instances in average)
and PAR-2 score ($-$57.7 in average).  The average clause size
reduction is consistent across all solvers. Each configuration also
exhibits different strength: $\allUipPure$ solved the most instances
with the best PAR-2 score on two solvers, $\allUipMin$ yields small
clauses, $\allUipIn$ solved the most SAT instances, and $\allUipAct$
has stable performance.

On the SAT 2017 race winner $\MapleSeven$, all four configurations of
$\stablealluip$ outperformed \oneuip learning by 12, 8, 5, and 2 instances,
respectively. $\allUipPure$ solved more UNSAT and SAT instances while
the other configurations improved on solving SAT instances. The clause
size reduction of $\stablealluip$ is more significant on $\MapleSeven$
than on to $\MapleBase$.

The SAT 2018 race winner$\MapleEightShort$ uses chronological
backtracking (CB) for long distance backtracks. Three out of four
$\stablealluip$ configurations outperformed \oneuip by 5, 4 an 4 instances,
respectively.

@@

@@

$\defaultcadical$ with \oneuip solved 249 instances, 5 more than the result from the SAT 2019 Race.  Applying $\allUipAct$ and $\allUipIn$ further improved the solved instance by 3 an 2, respectively.  The average learnt clause size of \oneuip on $\defaultcadical$ is much larger than other solvers' (101 vs 60) while the average clause size of $\stablealluip$ configurations are similar on all solvers.
